The Wolf in Sheep's Clothing\\ Subversive Adversarial Agent Identification

### 2016-08-04 article.tex
Cleans up bibliographies and solves issue where document wouldn't compile

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\graphicspath{{images/}}
\usepackage[backend=biber, style=ieee]{biblatex}
\addbibresource{jprefwolf.bib}
\addbibresource{mwrefwolf.bib}
\usepackage{amsmath}
\usepackage[final]{microtype}
\usepackage{caption}
\usepackage{glossaries}
\input{glossary.tex}
%\usepackage{hyperref}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

[INSERT RESULTS HERE]

\section{Conclusion}

We have presented three components from a larger chain of trust that is designed to ensure security of not only the agent itself, but also of the group of agents surrounding it.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

We would like to thank Professors Murat C. Cavusoglu, Russell C. Jackson and Tipakorn Greigarn and for their time, support and guidance.

\printbibliography

\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage[pdftex]{graphicx}
\graphicspath{{images/}}
\usepackage[backend=biber, style=ieee]{biblatex}
\addbibresource{jprefwolf.bib}
\addbibresource{mwrefwolf.bib}
\usepackage{amsmath} % For better math in tables and equations
\usepackage[final]{microtype} % Makes things look better in the end
\usepackage{glossaries} % Just here so I don't need to remove \gls{} from text when moving from my thesis
\input{glossary.tex}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

@@

\subsection{State Detection}
[INSERT RESULTS HERE]

\section{Conclusion}
We have presented three components from a larger chain of trust that is designed to ensure security of not only the agent itself, but also of the group of agents surrounding it.

@@

% use section* for acknowledgment
\section*{Acknowledgment}
We would like to thank Professors Murat C. Cavusoglu, Russell C. Jackson and Tipakorn Greigarn and for their time, support and guidance.

\printbibliography
\end{document}
